Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-23 paper.qmd
Updated Figure 16 a)

trimesh_removed_mnist <- ggplot() + 
  geom_segment(data = tr_from_to_df_mnist, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#33a02c",
               linewidth = 1) +
  geom_point(data = tsne_minst_scaled,
             aes(
               x = tSNE1,
               y = tSNE2
             ),
             alpha=0.1) +
  interior_annotation("a", sc_ltr_pos_mnist) +
  theme(aspect.ratio = 1)

>>>>

tsne_minst_scaled_temp <- tsne_minst_scaled |>
  mutate(cluster = if_else((tSNE1 <= 0.92) & (tSNE1 >= 0.75) & (tSNE2 <= 0.62) & (tSNE2 >= 0.44), "small_clust", "big_clust"))

trimesh_removed_mnist <- ggplot() + 
  geom_segment(data = tr_from_to_df_mnist, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#33a02c",
               linewidth = 1) +
  geom_point(data = tsne_minst_scaled_temp,
             aes(
               x = tSNE1,
               y = tSNE2,
               colour = cluster
             ),
             alpha=0.1)+
  scale_color_manual(values=c('#000000', '#e41a1c')) +
  interior_annotation("a", sc_ltr_pos_mnist) +
  theme(aspect.ratio = 1,
        legend.position = "none")
